Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-11 Grassmannian_cells.tex
Some final polishing in section 4

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item We consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,e)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
  \item We consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,e)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=\tilde\Sigma_2(\tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$. As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
\begin{proposition} 
  \label{indecomposables}
  Let $m\geq 1$ and $d(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
  The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
\end{proposition}
\begin{proof}
  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
  \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
    \Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}&\Ind\big(K(n),d(m+1,r)\big)}.\]
  As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto (V\cap M,(V+M)/M).\]
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.

Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe(\Gr_\tbff(M)\times \Gr_\tbfg(N))$. Then we have
$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following is proved in \cite[Section 3]{cefr}.
\begin{theorem}
  \label{vb}
  If the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it is an affine bundle over the image.
  In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}
%\begin{proof}\footnote{sketch, double-check}
%As $X$ and $Y$ are projective, they are compact. As the fibers are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$. This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
%\end{proof}

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above:
\begin{equation}
  \label{eq:truncated CC}
  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\begin{equation}
  \label{eq:truncated CC2}
  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi_{m,I,j}^{-1}(V,W)$.
  This gives rise to the following commutative diagram:  
  \[\xymatrix{
    0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
    0\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
    0\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j)/V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
    &0&0&0&}\]
  By Corollary~\ref{cor:perpendicular}, we have $\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j))=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_m(I,j)/V)=0$ as well.
  This yields the isomorphisms
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is zero.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0,\quad \Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since all quiver Grassmannians are points in this case.
  We establish the result for $m\ge2$ by proving the following more general statement:\\

@@

  Now suppose $|J|<n-1$.
  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.
  Thus we may assume $J\subsetneq I_0$.

@@

\begin{theorem}\label{celldec}The following holds:
\begin{enumerate}
\item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
\item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$. Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
\end{enumerate}
\end{theorem}
\begin{proof}
The first part follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover} taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation which can be proven using the same argument as in the proof of Lemma~\ref{le:lifts of transjectives}. The dual version for preinjective representations follows as $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$ respectively.

@@

\begin{corollary}
Let $X\in\rep K(n)$ be a direct sum of exceptional representations. Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces. In particular, this is true for all rigid representations of $K(n)$.
\end{corollary}
\begin{proof}
As every exceptional representation of $K(n)$ is either preprojective or preinjective, we have
$$X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sI_{k_i}$$
where we assume that $j_i\leq j_{i+1}$ and write
$$P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}I_{k_i}$$ 
for $r'\leq r$ and $s'\leq s$.

>>>>

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item We consider the lift $\tilde P_1$ satisfying $\udim(\tilde P_1)_{(1,e)}=1$ and $\udim(\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
  \item We consider the lift $\tilde P_2$ satisfying $\udim(\tilde P_2)_{(2,e)}=\udim(\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\udim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=\tilde\Sigma_2(\tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$. As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
\begin{proposition} 
  \label{indecomposables}
  Let $m\geq 1$ and $d(m,r)=\udim P_{m+1}-r\udim P_m$ with $0\leq r\leq n-1$.
  The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
\end{proposition}
\begin{proof}
  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
  \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
    \Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}&\Ind\big(K(n),d(m+1,r)\big)}.\]
  As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto \big(V\cap M,(V+M)/M\big).\]
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.

Let $\cG_{\tbff,\tbfg}:=\Psi^{-1}_\tbfe\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$. Then we have
$$\Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.$$
The map $\Psi_\tbfe$ restricts to morphisms of projective varieties
\[\Psi_\tbfe^{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following is proved in \cite[Section 3]{cefr}.
\begin{theorem}
  \label{vb}
  If the fiber dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$, then it is an affine bundle over the image.
  In particular, the existence of a cell decomposition of $\mathrm{Im}\big(\Psi_\tbfe^{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}
%\begin{proof}\footnote{sketch, double-check}
%As $X$ and $Y$ are projective, they are compact. As the fibers are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$. This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!
%\end{proof}

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above:
\begin{equation}
  \label{eq:truncated CC}
  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\begin{equation}
  \label{eq:truncated CC2}
  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi_{m,I,j}^{-1}(V,W)$.
  This gives rise to the following commutative diagram:  
  \[\xymatrix{
    0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
    &0&0&0&}\]
  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
  This yields the isomorphisms
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is zero.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\\

@@

  Now suppose $|J|<n-1$.
  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous and any cell decomposition will suffice.
  Thus we may assume $J\subsetneq I_0$.

@@

\begin{theorem}
  \label{celldec}
  The following hold:
  \begin{enumerate}
    \item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
    \item Let $X\in\rep K(n)$ be an indecomposable representation with dimension vector $(d,e)$ or $(e,d)$, where $(d,e)=\udim P_{m+1}-r\udim P_m$ for $m\geq 1$ and $\leq 0\leq r\leq n-1$.
      Then every quiver Grassmannian $\Gr_\bfe(X)$ has a cell decomposition into affine spaces.
  \end{enumerate}
\end{theorem}
\begin{proof}
  The first part follows by combining the results of Section~\ref{torusaction} and Theorems~\ref{thm:bb} and~\ref{cellscover}, taking into account that every preprojective representation of $\widetilde{ K(n)}$ is a lift of a preprojective representation (c.f.\ Lemma~\ref{le:lifts of transjectives}).
  The dual version for preinjective representations follows immediately since $\Gr_{\bfe}(P_m)\cong \Gr_{\udim P_m-\bfe}(I_m)$ and $\Gr_{\tbfe}(\tilde P_m)\cong\Gr_{\udim \tilde P_m-\tbfe}(\tilde I_m)$.

@@

\begin{corollary}
  Let $X\in\rep K(n)$ be a direct sum of exceptional representations.
  Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
  In particular, this is true for all rigid representations of $K(n)$.
\end{corollary}
\begin{proof}
  As every exceptional representation of $K(n)$ is either preprojective or preinjective, we have
  \[X=\bigoplus_{i=1}^rP_{j_i}\oplus\bigoplus_{i=1}^sI_{k_i},\]
  where we assume that $j_i\leq j_{i+1}$ and write
  \[P(r'):=\bigoplus_{i=1}^{r'} P_{j_i},\quad I(s'):=\bigoplus_{i=1}^{s'}I_{k_i}\]
  for $r'\leq r$ and $s'\leq s$.

  By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$.
  Consider the short exact sequence
  \[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
  By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition into affine spaces.
  Consider the Caldero-Chapoton map
  \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)=\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
  Now every subrepresentation $W$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
  Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
  Together these yield $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
  \[\dim\Hom(W,P_{j_{r'+1}}/U)=\langle W, P_{j_{r'+1}}/U\rangle\]
  for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
  By Theorem~\ref{vb}, this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition into affine spaces for every $1\leq r'\leq r$.
  By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.

  Finally consider the short exact sequence
  \[\ses{I(s)}{X}{P(r)}.\]
  As every quotient of $I(s)$ is preinjective and as every subrepresentation of $P(r')$ is preprojective, the same argument shows that every quiver Grassmannian attached to $X$ has a cell decomposition into affine spaces.
\end{proof}

As the $F$-polynomial of truncated preprojective representations only depend on the dimension vector, we may denote them by $F_{d(m,r)}$.
The description of the non-empty fibers in Proposition~\ref{fibers} together with Corollary~\ref{fpoly} and Theorem~\ref{celldec} yield the following:
\begin{corollary}
  For $m\geq 1$ and $0\leq r\leq n-2$, we have 
  \[F_{d(m,r)}=F_{d(m,r+1)}F_{\udim P_m}-x^{d(m,r)}F_{d(m-2,r)}.\]
\end{corollary}
